%
%  untitled
%
%  Created by Shravan Vasishth on 2012-04-02.
%  Copyright (c) 2012 __MyCompanyName__. All rights reserved.
%
\documentclass[a4paper]{article}

% Use utf-8 encoding for foreign characters
\usepackage[utf8]{inputenc}

% Setup for fullpage use
\usepackage{fullpage}

% Uncomment some of the following if you use the features
%
% Running Headers and footers
%\usepackage{fancyhdr}

% Multipart figures
%\usepackage{subfigure}

% More symbols
%\usepackage{amsmath}
%\usepackage{amssymb}
%\usepackage{latexsym}

% Surround parts of graphics with box
\usepackage{boxedminipage}

% Package for including code in the document
\usepackage{listings}




% If you want to generate a toc for each chapter (use with book)
\usepackage{minitoc}

% This is now the recommended way for checking for PDFLaTeX:
\usepackage{ifpdf}

%\newif\ifpdf
%\ifx\pdfoutput\undefined
%\pdffalse % we are not running PDFLaTeX
%\else
%\pdfoutput=1 % we are running PDFLaTeX
%\pdftrue
%\fi

\ifpdf
\usepackage[pdftex]{graphicx}
\else
\usepackage{graphicx}
\fi
\title{Current issues in sentence processing}
\author{Taught by Shravan Vasishth}

\date{\today}

\begin{document}

\ifpdf
\DeclareGraphicsExtensions{.pdf, .jpg, .tif}
\else
\DeclareGraphicsExtensions{.eps, .jpg}
\fi

\maketitle



\section{The basic stuff}

\begin{itemize}
	\item The course runs from  21 Oct to 16th Dec 2015.
%	\begin{itemize}
%		\item 01.05.2012 Maifeiertag
%		\item 17.05.2012 Christi Himmelfahrt
%		\item 27.05.2012 - 28.05.2012 Pfingsten
%	\end{itemize}	
	\item Day: Wednesdays
	\item Time: 10:25-12:50PM
	\item Place: Tokyo University, Building 8, Room 315	
\end{itemize}

We have  a total of 9 classes.

\section{Goals of this course}

We will be looking at some current issues relating to the cue-based retrieval theory and predictive processes in sentence comprehension.

\section{Papers to be covered}

There will be one further paper by Shota Momma et al, which does not yet exist but is being prepared in Maryland as we speak.

Note that I sometimes tend to go off on a tangent and discuss related studies, so don't be surprised if we don't get to discuss all the papers on the list. The list below is only suggestive.

\begin{enumerate}
\item Oct 21: Introduction

\item Oct 28: \cite{engelmann2015determinants}

\item Nov 4: \cite{traxler2014trends}, \cite{LevyKeller2012} 

\item Nov 11: \cite{linzen2015uncertainty}, \cite{Jaegeretal2015}

\item Nov 18: \cite{VSLK08}, \cite{FrankEtAl2014}, \cite{bader2015interference}

\item Nov 25: \cite{omaki2015hyper}, \cite{mommatiming}


\item Dec 2: \cite{chow2013no}, \cite{chowbag}

\item Dec 9: Momma paper (to be provided)

\item Dec 16: Closing discussion

 
\end{enumerate}


The papers will be made available from the course page. There are other related readings, which I can release on demand.

\section{Grading}

Grading will be based on a short report (2-3 pages at most) on one or more of the papers discussed in the course.  The report can be in Japanese, German, French, English, or Hindi.  Extra credit will be given for original ideas/proposals in the summary, and for class participation. If you come up with a new experiment design that attempts to resolve an open question, then you are very likely to get a high score.

\section{In the classroom}

\begin{itemize}
\item As a general rule, please do not chat with each other while I am talking or while we are discussing something in class.
\item I expect active participation, which means asking questions and discussing the various issues that come up. 
\item  Please \textbf{do not} use cell phones or computers to chat, message or call anyone, and do not check your email or send or receive SMSes. In some cases people may have to keep their phone on due to a sick child or something like that; in that case, please get permission from me before start of class.
\item Please come to class on time so that we can start punctually at 10:25AM.
\end{itemize}

\bibliographystyle{unsrt}
\bibliography{currentissues}
\end{document}
